NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-19 paper/Chapters/Chapter4.tex
adding strengths in the discussion

>>>>

Strengths of this study include the large, nationally representative sample of men and women in the UK. We applied a novel, objective approach using MLCA to examine the carbohydrate eating patterns while using standardised criteria to determine the numbers of latent classes. The process of finding the classifications through model-based, data-driven procedure minimises reliance on researchers' preconcieved notions of eating patterns. Eating patterns were determined from 4 consecutive days of well-designed, fully-examined food diaries. MLCA correctly accounted for the multilevel structure of the data which means that the 4-day diet diaries were nested within the participants. Our findings also captured the day-to-day variation of following different carbohydrate eating patterns within individuals. Moreover, the examination of associations between the individual level carbohydrate eating patterns and hypertension, BMI, abdominal obesity were conducted correctly considering the probability of participant selection and the clustered survey design. Health outcomes such as weight, height, waist circumferences, and blood pressure, diabetes status were measured by trained nurses and blood tests which could also minimise the misclassification and under-reporting of these measurements.
